\cvsection[page1sidebar]{Experience}
\cvevent{Lead Analyst -- GTM Strategy and Planning}{Confluent India Pvt Ltd}{Jan 2023 - Apr 2024}{Bangalore, India}
\begin{itemize}
  \item Lead and mentor a team of 4 senior analysts and analysts.
  \item Collaborate with global leadership for design and implementation of comprehensive pipeline generation dashboard. This interactive tool tracks individual and team performance, increasing \textbf{13\%} pipeline revenue, by assisting stakeholders with \textbf{near real-time insights} to optimize sales strategies.
  \item Developed \textbf{user driven, self-service platform} to track metrics for Quarterly Business Reporting to tracking progress in metrics daily over longer time-frames (daily, weekly, monthly) with \textbf{removal of all manual interventions}.
  \item Partnered with the data engineering team to design and maintain new data pipelines in \textbf{Apache Airflow} to fetch previously missing or newly added attributes to \textbf{Salesforce}. Maintained git repository to enhance created data pipelines for seamless reporting resulting in runtime reduction by \textbf{8\%}.
\end{itemize}
{\footnotesize{ \cvtag{Tableau} \cvtag{Python} \cvtag{SQL (BigQuery)} \cvtag{Apache-Airflow} \cvtag{Salesforce} }}


\vspace{2pt}
\cvevent{Lead Applied Data Scientist}{Tesco Business Services}{Jun 2022 - Jan 2023}{Bangalore, India}
\begin{itemize}
  \item Led a team of 4 analysts to unveil previously unidentified profit leakages through a comprehensive driver model analysis. This data-driven approach pinpointed hidden loss factors within retail operations, enabling implementation of targeted mitigation strategies. The resulting improvements yielded a combined profit increase of \textbf{£2 million (GBP)} across Central European stores.
  \item Spearheaded a new initiative focused on \textbf{demand forecasting} and \textbf{demand sensing} through \textbf{ARIMA/SARIMA} across SKU x Channel x Location combinations, factoring in promotions, weather patterns and industry events to predict future demand, improving Merchandise procurement by \textbf{6\%}.
\end{itemize}
{\footnotesize{ \cvtag{Tableau} \cvtag{SQL (Hadoop, Hive, Spark)} \cvtag{Python} \cvtag{pandas} \cvtag{numpy} \cvtag{statmodels}}}

\vspace{2pt}
\cvevent{Senior Applied Data Scientist}{Tesco Business Services}{Dec 2020 - Jun 2022}{Bangalore, India}
\begin{itemize}
  \item Led team of analysts and category planners in collecting data and improving ways to measure KPIs to capture the most relevant and updated information.
  \item Developed an \textbf{End-2-End automated Decision Cockpit} for Central Europe execs and Category planners. This cockpit keeps track of various crucial metrics to understand the health of the categories along with devising new strategies to improve the \textbf{CPS (Customer Priority Score)} of each category.
  \item Analyzed the \textbf{Hypermarket de-growth} in CE region to reduce the loss due to Customer switching and increase of competition in various demographics. The analysis is projected to reduce Customer switching by \textbf{2\%} in Czech Republic market.
  \item Create multiple automation in \textbf{Python} and \textbf{VBA} to enable automated reporting so as the decrease man hours. Benefits of \textbf{weekly 30+ man hours} were observed by the change.
\end{itemize}
{\footnotesize{ \cvtag{Tableau} \cvtag{SQL (Hadoop, Hive, Spark)} \cvtag{Python} \cvtag{VBA} }}


\vspace{2pt}
\cvevent{Senior Data Scientist}{Affine Analytics}{Jul 2019 - Dec 2020}{Bangalore , India}
\begin{itemize}
  \item Prioritized \textbf{website ad banners} using \textbf{regression models} in \textbf{python}. Deployed the model for revenue simulations in Excel, and optimized the underlying data pipeline (ETL) to reduce cloud costs by half.
  \item Built \textbf{anti-cheat systems} using BigQuery to track and remove cheaters, \textbf{designed and tested} new in-game features, and inspected player behavior to uncover monetization opportunities.
  \item Analyzed potential customer segments for upcoming games, defining and quantifying their characteristics to inform targeted marketing strategies.
\end{itemize}
{\footnotesize{ \cvtag{SQL (BigQuery)} \cvtag{Apache-Airflow} \cvtag{Python} \cvtag{Periscope} \cvtag{SQL (Snowflake)} \cvtag{VBA} }}


\vspace{2pt}
\cvevent{Asst. Manager - Analytics}{WNS Global Services}{Dec 2018 - Jun 2019}{Bangalore, India}
% \begin{itemize}
%   \item Leveraged machine learning \textbf{(Linear Regression, SVM, Neural Networks)} to target customers, analyzed daily operations with F\&B dashboards, and planned \& analyzed marketing campaigns to optimize ROI, sales growth, customer retention, and channel performance.
% \end{itemize}


\vspace{2pt}
\cvevent{Analyst}{Ipsos Research Pvt. Ltd}{Jun 2016 - Nov 2018}{Bangalore, India}
% \begin{itemize}
  % \item Analyzed marketing data and built pricing optimization tools in Excel using VBA using Market Mix Modeling and various pricing models to maximize client revenue across diverse industries (food, retail, etc.).
% \end{itemize}


% \vspace{2pt}
% \cvevent{ Asst. Systems Admin }{Master Engg. Concern }{Jul 2011 - May 2014}{Kolkata, India}
