% Original Dates: OriginalDates | False Dates: FalseDates
% SeniorAssociate | DataScientist | SeniorAnalyst
%------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------------
\documentclass[a4paper]{resume_001} % a4paper for A4
%------------------------------------------------------------------------------
%  PERSONAL INFORMATION
%------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving
% the command, e.g. \cvnumberphone{}

\cvname{Ankit} % Your name
\cvjobtitle{Haldar} % Job title/career
\cvdate{} % Date of birth
\cvmail{ankithaldar@gmail.com} % email
\cvnumberphone{(+91) 9742293728} % Phone number
\cvsite{haldarankit} % Personal website
\cvaddress{Bengaluru, \textit{Karnataka}}

%------------------------------------------------------------------------------
\begin{document}
%------------------------------------------------------------------------------
%  Education
%------------------------------------------------------------------------------
\education{
{\boldcolor{MBA - PGP Business Management}}\\ Praxis B-School | \textit{2014 - 2016}\\ %FalseDates
% {\boldcolor{MBA - PGP Business Management}}\\ Praxis B-School | \textit{2013 - 2015}\\ % OriginalDates
\smallskip
{\boldcolor{B.Sc (IT)}} | \textit{2008 - 2011} % FalseDates
% {\boldcolor{B.Sc (IT)}}\\ Kuvempu Univ | \textit{2007 - 2011} % OriginalDates
}
\bigskip
%------------------------------------------------------------------------------
% Skill bar section, each skill must have a value between 0 an 6 (float)
%------------------------------------------------------------------------------
\skills{
{\boldcolor{Hard Skills}}: Statistics, Machine Learning, A/B Testing\\
{\boldcolor{Languages}}: SQL, Python, VBA, Google App Script, C, C++, \LaTeX\\
{\boldcolor{Databases}}: Hive, Google-BigQuery, Snowflake, Oracle, MSSQL, SQLite\\
{\boldcolor{ETL Tools}}: Apace-Airflow\\
{\boldcolor{Visualization}}: Tableau, Periscope, PowerBI\\
{\boldcolor{Others}}: Web Scraping, Google Office Suites, MS Office Suites, Advanced Excel, Git, Github\\
{\boldcolor{OS}}: Ubuntu, Fedora\\
}
\bigskip

\interests{}
% \interests{\textit{Participating and learning from \boldcolor{Kaggle} competitions}}
\bigskip

\orginitiatives{\boldcolor{{Leading}} a team of 7, with resource allocation, ensuring error free deliverables.\\
\smallskip
\boldcolor{{Mentor}} two batches of interns on summer project (Affine, Tesco).\\
\smallskip
Conduct \boldcolor{{training}} sessions for freshers on analytical tools (\boldcolor{SQL, Python, Advanced Excel \& VBA})\\
\smallskip
\boldcolor{{Interview}} potential candidates (Affine, Tesco).
% \smallskip
% ITC Project in one line
}
\bigskip

\awards{
\textit{\boldcolor{Star of the Month}} at Tesco Business Services - Enterprise Analytics\\
\textit{\boldcolor{Transformer of the Month}} at Affine Analytics Pvt. Ltd.\\
\textit{\boldcolor{Fast Start Star}} at Ipsos Research Pvt. Ltd.}
\bigskip

\hobbies{Football (\textit{College Captain}), Swimming, Cycling}
\bigskip

\languages{
English: Read | Write | Speak\\
Hindi  : Read | Write | Speak\\
Bengali: Read | Speak
}
%------------------------------------------------------------------------------
% Skill text section, each skill must have a value between 0 an 6
%------------------------------------------------------------------------------
\makeprofile % Print the sidebar
%------------------------------------------------------------------------------
% \section{Profile}
% \textit{Data Analyst with proven expertise in business problem solutioning, dash-boarding, reporting and stakeholder management.}

\section{Work Experiences}

\begin{twenty} % Environment for a list with descriptions
    %\twentyitem{<dates>}{<title>}{<location>}{<description>}

    \twentyitem{\small Dec 2020\\\small Present}{Lead Decision Analyst}{Tesco, \textit{Bengaluru}}{
    % {\textbf{Senior Decision Analyst (Dec'20 - May'20)}}\\
    \vspace{-3mm}
    \begin{itemize}[leftmargin=*]
        \item Analysed the \bold{Hypermarket de-growth} in CE region to reduce loss due to Customer switching amd increase of competition in various demographics.
        \item Develop decision enabling \textbf{Tableau} dashboards and underlying automations for the dashboard to be self updatable.
        \item Create automations to enable automated reporting so as the decrease the time taken to generate the reports.
        \item Understanding drivers of loss unknown to retailer, and minimze them using a driver model generating higher profits of £2 million (GBP) for combined stores in Central Europe.
    \end{itemize}
    \textit{\small Tools: \boldcolor{Tableau, SQL (Hadoop, Hive, spark), Python, PySpark}}

    }

    \twentyitem{\small Jul 2019\\\small Dec 2020}{Senior Analyst}{Affine Analytics, \textit{Bengaluru}}{ %SeniorAssociate OriginalDates
    % \twentyitem{\small Jul 2019\\\small Dec 2020}{Data Scientist}{Affine Analytics, \textit{Bengaluru}}{ %DataScientist FalseDates
    % \twentyitem{\small Jul 2019\\\small Dec 2020}{Senior Analyst}{Affine Analytics, \textit{Bengaluru}}{%SeniorAnalyst  FalseDates
    {\textbf{Mobile Game developer (May'20 - Dec'20)}}\\
    \vspace{-3mm}
    \begin{itemize}[leftmargin=*]
        \item Develop \textit{Apache-Airflow} based ETL process in \textit{Google Cloud Platform (GCP)} for tracking in-game metrics. Analysed GCP usage and modified ETL process to reduce GCP costs by almost 50\%.
        \item Built highly customised \textit{Periscope} dashboards for stakeholders to understand game performance.
        \item Conceptualize new in-game features and run \textit{A/B Tests}. Analyse \textit{A/B Test} impact and suggest implementation of feature.
        \item Undertake adhoc investigations to understand player behaviour. Discover new customer segments with monetization potential.
        \item Implement new algorithm to track and eliminate/block cheaters from the game.
    \end{itemize}
    \textit{\small Tools: \boldcolor{SQL (BigQuery), Apache-Airflow, Python, Periscope, Google Docs Suite, Google Apps Script}}
    \medskip\\
    {\textbf{Gaming Console Manufacturer (Jul'19 - May'20)}}\\
    \vspace{-3mm}
    \begin{itemize}[leftmargin=*]
        % \item Implemented a regression model for forecasting of sales for upcoming major games with MAPE less than 15\% and used Time series in forecasting sales of franchise games which further helped in deciding partnership with major game studios.
        \item Apply regression modeling techniques to prioritize advertisement banners on store website to capture consumer attention boosting sales.
        \item Implement model into product to simulate revenue based on advertisement priority.
        % \item Create reports on requests like used console and disk analysis, product churn and analyse performance and impact of promotions.
        \item Analyse potential customer targeting strategies for upcoming titles by defining and quantifying different segments of potential audience.
        % \item Create \textit{Tableau} dashboards for various business verticals that enabled clients to analyse business performance.
    \end{itemize}
    \textit{\small Tools: \boldcolor{SQL (Snowflake), Python, VBA, Excel, Tableau}}
    }

    \twentyitem{\small Dec 2018\\\small Jun 2019}{Asst. Manager - \textit{Analytics}}{WNS Global Services, \textit{Bengaluru}}{
    \vspace{-3mm}
    \begin{itemize}[leftmargin=*]
        \item Analysis of daily operations through dash-boarding for a Food \& Beverage chain.
        \item Plan campaigns and build post-campaign analysis reports to understand ROIs, sales growth, customer turnover and channel performance.
        \item Identifying potential customers to upscale by creating customized offers through machine learning techniques (\textit{Linear Regression, SVM, Neural Networks}).
    \end{itemize}
    \textit{\small Tools: \boldcolor{SQL (Oracle), Python, Tableau, Advanced Excel}}
    }

    \twentyitem{\small Jun 2016\\\small Nov 2018}{Analyst}{Ipsos Research Pvt. Ltd., \textit{Bengaluru}}{
    \vspace{-3mm}
    \begin{itemize}[leftmargin=*]
        \item Market Mix Modeling projects on leading US CPG, Retail, E-Business, Restaurant, Pharmaceuticals, Sports Goods, Automobile to allocate investment in different marketing attributes to optimize effectiveness, ROI of each vehicle.
        \item Implement client deliverable products based on pricing models for simulation of price change leading to changes in units and revenue.
    \end{itemize}
    \textit{\small Tools: \boldcolor{SQL (MSSQL), Python, Tableau, VBA, Advanced Excel}}
    }

    % \twentyitem{\small Jul 2010\\\small May 2013}{Asst. Systems Admin}{Master Engg. Concern, \textit{Kolkata}}{% OriginalDates
    \twentyitem{\small Jul 2011\\\small May 2014}{Asst. Systems Admin}{Master Engg. Concern, \textit{Kolkata}}{% FalseDates
    \vspace{-3mm}
    % \begin{itemize}[leftmargin=*]
    %     \item Built \textit{Python and SQLite} based automated letter tracking system.
    %     \item Collect daily project status from field supervisors and engineers to generate reports stake-holders.
    %     % \item Create project initiation \& project consumable purchase reports.
    %     % \item Act as a Liaison between different departments.
    %     % \item Keeping the clients informed monthly about the progress and collect updates on change in project scope.
    %     % \item Attend project meetings, minute the meetings and pass on information to all relevant departments.
    % \end{itemize}
    \textit{\small Tools: \boldcolor{SQL (SQLite), Python, Excel}}
    }

\end{twenty}
% \section{Internships}
% \begin{twenty} % Environment for a list with descriptions
%   \twentyitem{Summer\\2014}{Summer Intern}{ITC Sonar Hotels, \textit{Kolkata}}{% OriginalDates
%   \twentyitem{Summer\\2015}{Summer Intern}{ITC Sonar Hotels, \textit{Kolkata}}{% FalseDates
%   \begin{itemize}[leftmargin=*]
%     \item Summer Intern in quality management applying Six Sigma Techniques to improve laid out hotel processes.
%     \item Breakdown processes into measurable parameters to analyse performance of each process.
%   \end{itemize}
%   }
% \end{twenty}
%----------------------------------------------------------------------------------------
%  OTHER INFORMATION
%----------------------------------------------------------------------------------------
%\section{Projects}
%\subsection{\textit{Affine Analytics}}
%\\
%\subsection{\textit{Ipsos Research Pvt. Ltd}}
%----------------------------------------------------------------------------------------
\end{document}
