\resumeSubheading
  {Lead Data Analyst -- Insights and Analytics}{Jan 2023 -- Apr 2024}
  {Confluent India Pvt. Ltd.}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{\textbf{Managed and led a team of 4} located in India, overseeing day-to-day activities, building road-maps, and ensuring alignment with project goals and timelines.}
    \resumeItem{Analyzed data to identify \textbf{patterns, trends, and insights} that informed business strategies, resulting in a 15\% increase in customer retention.}
    \resumeItem{Developed and maintained \textbf{dashboards, reports, and visualizations} using \textbf{Tableau} to communicate findings to stakeholders, improving reporting efficiency by 25\%.}
    \resumeItem{Conducted \textbf{segmentation analysis} to understand different groups and their behaviors, leading to targeted marketing campaigns that increased sales by 20\%.}
    \resumeItem{Collaborated with marketing, product, and sales teams to provide \textbf{data-driven recommendations}, enhancing cross-departmental decision-making.}
    \resumeItem{Monitored and analyzed \textbf{key performance indicators (KPIs)} related to customer satisfaction, retention, and acquisition, contributing to a 10\% improvement in customer satisfaction scores.}
    \resumeItem{Utilized advanced analytics techniques, including \textbf{predictive modeling and machine learning} in \textbf{Python}, to forecast behavior and trends, aiding in strategic planning.}
    \resumeItem{Leveraged \textbf{Advanced SQL} to extract and analyze sales data, identifying opportunities for process improvements that increased sales efficiency by 18\%.}
    \resumeItem{Developed comprehensive sales reports and dashboards in \textbf{Tableau}, enabling real-time performance tracking and strategic planning.}
    \resumeItem{Conducted detailed segmentation analysis, leading to the implementation of targeted sales strategies that boosted sales by 22\%.}
    \resumeItem{Collaborated with the sales team to provide \textbf{data-driven recommendations}, optimizing sales operations and driving a 15\% increase in revenue.}
    \resumeItem{Monitored and analyzed sales \textbf{KPIs}, contributing to a 12\% increase in sales team performance.}
    \resumeItem{Designed and conducted surveys and focus groups to gather feedback, providing valuable insights for product development and marketing strategies.}
    \resumeItem{Presented findings and recommendations to senior management and other stakeholders in a clear and compelling manner, facilitating informed decision-making.}
    \resumeItem{Stayed up-to-date with industry trends and best practices in analytics and insights, ensuring the continuous improvement of data analysis processes.}
  \resumeItemListEnd
  \textit{\small Tools: \textbf{Tableau, Python, SQL(Bigquery), Airflow, Git}}
