\resumeSubheading
  {Senior Data Analyst}{Jul 2019 - Dec 2020}
  {Affine Analytics}{Bangalore, India}
  \resumeItemListStart[leftmargin=0.0in, label={}]

    % Part 2
    \resumeItem{Client: \textbf{Mobile Game developer (May 2020 - Dec 2020)}}
      \resumeItemListStart
        \resumeSubItem{Develop \textbf{Apache-Airflow} based ETL process in \textbf{Google Cloud Platform (GCP)} for tracking in-game metrics. Analysed GCP usage and modified ETL process to reduce GCP costs by almost 50\%.}
        \resumeSubItem{Developed tailored \textbf{Periscope} dashboards, providing stakeholders with a \textbf{comprehensive and dynamic view of key game performance indicators (KPIs)}. These interactive visualizations empower data-driven decision making to optimize player engagement and achieve strategic business objectives.}
        \resumeSubItem{Develop innovative in-game features through rigorous ideation and iterative testing methodologies. Analyze the quantitative and qualitative data gleaned from \textbf{A/B tests} to assess player engagement and potential impact on key performance indicators (KPIs). Based on these insights, formulate a data-driven recommendation for feature implementation.}
        % \vspace{-10pt}
        \resumeSubItem{Employ ongoing \textbf{investigative analytics} to gain a comprehensive understanding of \textbf{player behavior}. Leverage this data to identify and segment previously unknown customer cohorts with high monetization potential.}
        \resumeSubItem{Integrate a sophisticated \textbf{new anti-cheat detection algorithm} to proactively identify and mitigate unauthorized game-play behavior, fostering a fair and competitive environment for all players.}
      \resumeItemListEnd
      \vspace{5pt}
      \textit{\small Tools: \textbf{SQL (BigQuery), Apache-Airflow, Python, Periscope, Google Docs Suite, Google Apps Script}}

    % Part 1
    \smallskip
    \resumeItem{Client: \textbf{Gaming Console Manufacturer (Jul 2019 - May 2020)}}
      \resumeItemListStart
        \resumeSubItem{Implemented a regression model for forecasting of sales for upcoming major games with \textbf{MAPE less than 15\%} and used \textbf{Time series} in forecasting sales of franchise games which further helped in deciding partnership with major game studios.}
        \vspace{-10pt}
        \resumeSubItem{Apply \textbf{regression modeling} techniques to \textbf{prioritize advertisement banners} on store website to capture consumer attention boosting sales. Integrate a data-driven revenue forecasting model into a product, empowering marketing VPs to conduct scenario simulations and optimize advertisement prioritization strategies for maximum revenue generation.}
        \resumeSubItem{Create reports on requests like used console and disk analysis, product churn and analyse performance and impact of promotions.}
        \resumeSubItem{Analyse potential customer targeting strategies for upcoming titles by defining and quantifying different segments of potential audience.}
        \resumeSubItem{Create \textbf{Tableau} dashboards for various business verticals that enabled clients to analyse business}
      \resumeItemListEnd
      \vspace{5pt}
      \textit{\small Tools: \textbf{SQL (Snowflake), Python, VBA, Excel, Tableau}}
  \resumeItemListEnd
\medskip
