\resumeSubheading
  {Senior Data Scientist}{Dec 2018 - Dec 2020}
  {Affine Analytics}{Bangalore, India}
  \resumeItemListStart[leftmargin=0.0in, label={}]

    % Part 2
    \resumeItem{Client: \textbf{Mobile Game developer (May 2020 - Dec 2020)}}
      \resumeItemListStart
        \resumeSubItem{Develop \textbf{Apache-Airflow} based ETL process in \textbf{Google Cloud Platform (GCP)} for tracking in-game metrics. Analysed GCP usage and modified ETL process to reduce GCP costs by almost 50\%.}
        \resumeSubItem{Developed tailored \textbf{Periscope} dashboards, providing stakeholders with a \textbf{comprehensive and dynamic view of key game performance indicators (KPIs)}. These interactive visualizations empower data-driven decision-making to optimize player engagement and achieve strategic business objectives.}
        \resumeSubItem{Develop innovative in-game features through rigorous ideation and iterative testing methodologies. Analyze the quantitative and qualitative data gleaned from \textbf{A/B tests} to assess player engagement and potential impact on key performance indicators (KPIs). Based on these insights, formulate a data-driven recommendation for feature implementation.}
        \resumeSubItem{Employ ongoing \textbf{investigative analytics} to gain a comprehensive understanding of \textbf{player behavior}. Leverage this data to identify and segment previously unknown customer cohorts with high monetization potential.}
        \resumeSubItem{Integrate a sophisticated \textbf{new anti-cheat detection algorithm} to proactively identify and mitigate unauthorized game-play behavior, fostering a fair and competitive environment for all players.}
      \resumeItemListEnd
      \vspace{5pt}
      \textit{\small Tools: \textbf{SQL (BigQuery), Apache-Airflow, Python, Periscope, Google Docs Suite, Google Apps Script}}

    % Part 1
    \smallskip
    \resumeItem{Client: \textbf{Gaming Console Manufacturer (Jul 2019 - May 2020)}}
      \resumeItemListStart
        \resumeSubItem{Implemented a regression model for forecasting sales for upcoming major games with \textbf{MAPE less than 15\%} and used \textbf{Time series} in forecasting sales of franchise games which further helped in deciding partnerships with major game studios.}
        \vspace{-10pt}
        \resumeSubItem{Apply \textbf{regression modeling} techniques to \textbf{prioritize advertisement banners} on the store website to capture consumer attention boosting sales. Integrate a data-driven revenue forecasting model into a product, empowering marketing VPs to conduct scenario simulations and optimize advertisement prioritization strategies for maximum revenue generation.}
        \resumeSubItem{Create reports on requests like used console and disk analysis, product churn, analyze performance, and impact of promotions.}
        % \vspace{-10pt}
        \resumeSubItem{Analyse potential customer targeting strategies for upcoming titles by defining and quantifying different segments of potential audience.}
        \resumeSubItem{Create \textbf{Tableau} dashboards for various business verticals that enabled clients to analyze business}
      \resumeItemListEnd
      \vspace{5pt}
      \textit{\small Tools: \textbf{SQL (Snowflake), Python, VBA, Excel, Tableau}}

    % Part 0
    \smallskip
    \resumeItem{Client: \textbf{Global Food \& Beverage Retailer (Dec 2018 - Jul 2019)}}
      \resumeItemListStart
      \resumeSubItem{Extensively used SQL/Python to mine and structure data from multiple loyalty \& transactional tables to automate \& derive KPIs for a 5M+ loyalty customer base.}
      \resumeSubItem{Developed Tableau \& Excel-based dashboards to report Customer-Beverage Aﬃnity \& Basket preferences, Store performance analysis, Loyalty Metrics Dashboard, Collaboration with third-party services, etc.}
      \resumeSubItem{Evaluated potential drawbacks of the Loyalty team's collaboration with an insurance-based third-party service, which set up the grounds for renegotiating their deal, saving up to £2.5M annually}
      \resumeSubItem{Performed Look-alike customer proﬁling and segmentation using RFM metrics and K means clustering, setting up a framework for Test vs Control Post Campaign/Event Analysis}
      \resumeSubItem{Used ARIMA and Exponential Smoothing models to determine baseline sales \& assess the incremental impact of the launch of Red cups during the Holiday season (UK market)}
      % \resumeSubItem{Analysis of daily operations through dash-boarding for a Food \& Beverage chain.}
      % \resumeSubItem{Plan campaigns and build post-campaign analysis reports to understand ROIs, sales growth, customer turnover and channel performance.}
      % \resumeSubItem{Identifying potential customers to upscale by creating customized offers through machine learning techniques (\textit{Linear Regression, SVM, Neural Networks}).}
      \resumeSubItem{Create a fully automated data extractor \& feeder by scraping data for franchises from multiple websites using \textbf{python selenium}.}
      \resumeItemListEnd
      \vspace{5pt}
      \textit{\small Tools: \textbf{SQL (Oracle), Python, Tableau, Excel, VBA}}
  \resumeItemListEnd
\medskip
