\resumeSubheading
  {Analyst}{Jun 2016 -- Nov 2018}
  {Ipsos Research Pvt. Ltd. (Marketing Management Analytics)}{Bangalore, India}
  \resumeItemListStart
    % \resumeItem{Market Mix Modeling projects on leading US CPG, Retail, E-Business, Restaurant, Pharmaceuticals, Sports Goods, Automobile to allocate investment in different marketing attributes to optimize effectiveness, ROI of each vehicle.}

    % \resumeItem{Worked as Analyst with IPSOS Research Pvt. Ltd. at Marketing Management Analytics (MMA) wing. Assigned to provide clients with useful business insights from a mix of the following studies (using SQL, R and SAS)}
    \resumeItem{Data Validation, Data Analysis – Ensuring reasonableness of data. Deciding and transforming raw data into model data.}
    \vspace{-10pt}
    \resumeItem{Market Mix Modelling – Multivariate time series Modelling for better understanding of revenue derived by different marketing components.}
    \resumeItem{Pricing Analysis – Log-Linear Models are generally constructed for Pharmaceutical clients to deep dive into the market scenario regarding what should be the optimal price for the newly launched medicine or post launch analysis and how the sales can be pushed up.}
    \resumeItem{Effectiveness Analysis - Fragmenting effects of the marketing drivers to a more granular level (eg: Market/DMA level insights)}
    \resumeItem{ROI Analysis \& Optimization – Based on ROI, MROI, Optimization of Advertisement tactic suggesting client to decide their adverting spending pattern to maximize profit.}
    \resumeItem{Implement client deliverable products based on pricing models for simulation of price change leading to changes in units and revenue.}
    % \resumeItem{}
  \resumeItemListEnd
  \textit{\small Tools: \textbf{SQL (MS-SQL), Python, Tableau, VBA, Advanced Excel, SAS, R}}
